Poster Data Analysis

### 2018-09-12 notebooks/poster_analysis.Rmd
updated dendrogram

## Heatmap plot
This plot represents the individual resistance mechanisms (x-axis) present in each isolate (y-axis), for each animal species (colors). Grey squares represent genes/mutations that ARIBA flagged as bad quality in their report. Dark color indicates presence, while the light color indicates absence.
```{r fig.height=30, fig.width=10, message=FALSE, warning=FALSE}
# Adjust MLST data frame
sequence_types_adjusted <- mlst_results %>%
  mutate_all(funs(gsub("\\*", "", .))) %>%
  select(-ST)

>>>>

## Heatmap plot
This plot represents the individual resistance mechanisms (x-axis) present in each isolate (y-axis), for each animal species (colors) and sequence type (dendrogram). Grey squares represent genes/mutations that ARIBA flagged as bad quality in their report. Dark color indicates presence, while the light color indicates absence. Part of the code below is taken from https://gist.github.com/scwatts/8c32d8f6dc44e352d89ae3de5f3a1125.
```{r fig.height=30, fig.width=10, message=FALSE, warning=FALSE}
# Adjust MLST data frame
sequence_types_adjusted <- mlst_results %>%
  mutate_all(funs(gsub("\\*", "", .))) %>%
  select(-ST)
